---
title: "LR tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

To use the function 'LR':

```{r setup}
library(LR)
library(ISLR)
```

```{r}
LR(swiss,c("Fertility", "Agriculture", "Examination", "Education") ,"Infant.Mortality")
```

To use the function "LR":with LR(data,x,y), using data "Auto" from package "ISLR"

```{r}
data <- Auto
x <- c("cylinders", "displacement", "horsepower", "weight", "acceleration", "year", "origin")
y <- "mpg"
```


The output of LR includes the general output and divided output, if you only need a part of the output, use"$"

If you need residuals:

```{r}
residuals <- LR(Auto, x, y)$residuals
print(residuals)
```

If you need coefficients sheet with standard error, t-value and p-value :

```{r}
coefficients <- LR(Auto, x, y)$coefficients
print(coefficients)
```

If you need 95% confidence intervals, you do not need "confint()" function for the model as it is contained in this LR function:

```{r}
CI_95 <- LR(Auto, x, y)$CI_95
print(CI_95)
```

If you need Multiple R-squared:

```{r}
MRS <- LR(Auto, x, y)$MRS
print(MRS)
```

If you need Adjusted R-squared:

```{r}
ARS <- LR(Auto, x, y)$ARS
print(ARS)
```

If you need F-statistic:

```{r}
F_statistic <- LR(data, x, y)$F_statistic
print(F_statistic)
```

If you need p-value for F-statistic:

```{r}
p_value_F <- LR(data, x, y)$p_value_F
print(p_value_F)
```

If you need a general output:
```{r}
general <- LR(data, x, y)$general
cat(paste(general, collapse = "\n"))
```


Time that will cost:
```{r}
system.time(summary(lm(mpg ~ cylinders + displacement + horsepower + weight + acceleration +
                         year + origin, data = Auto)))

system.time(LR(Auto,x,y))
```

